Identifying Effective Motivational Interviewing Sequences Using Automated Pattern Analysis

### 2018-04-13 jhir/latex-manuscript/manuscript.tex
update TABLES

\multicolumn{4}{l}{Counselor} \\

@@

\rowcolor{lightgraycol}
\multicolumn{4}{l}{Patient} \\
CT & Change Talk & Statements that express the patient’s desire, ability, reasons, need for, or commitment to (intentions, plans, and action steps) changing their behavior & ``I will try to buy less junk food.''\\
ST & Sustain Talk & Statements that express the patient’s desire, ability, reasons, need for, or commitment to (intentions, plans, and action steps) to maintain the status quo or not change their behavior  & ``I didn’t get to the gym this week.''\\
HUPO	 & High uptake other & An utterance that develops the topic of the conversation but is about non-target behaviors or interruptions & ``Yeah because the mentor comes and they take off and they go someplace for a little while.''\\
HUPW & High uptake weight & A turn that does develop the topic of the conversation. High Uptake statements include: weight related statements about actions of commitment, change talk, and ambivalence that occurred in the past, patient questions to the counselor, and session interruptions by persons who are not an active part of the treatment session. & ``Support is always good.  You know that’s a key factor.  Mm-hmm.''\\
LUP & Low uptake  & an utterance that does not develop the topic of conversation but still allows it to continue & ``Mm-hmm.  Right.''\\
\hline
\end{longtable}
\end{small}

@@

\begin{sidewaystable}
\vspace{15\baselineskip}

\caption{Hidden Markov Model Emission Matrices}
\label{tab:emission}
\begin{tabularx}{\textwidth}{lllllllll}
\hline\noalign{\smallskip}
first & second & third & first & second & third & first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number & number & number & number & number & number & number\\
number & number & number & number & number & number & number & number & number\\
\noalign{\smallskip}\hline
\end{tabularx}

@@

\caption{Hidden Markov Model Transition Matrices}
\label{tab:transition}  
\begin{tabularx}{\textwidth}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabularx}
\end{sidewaystable}

@@

\begin{table}
\begin{threeparttable}
\caption{Frequent communication patterns in successful and unsuccessful patient-counselor communication sequences.}
\label{tab:patterns}   
\begin{tabularx}{\textwidth}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number number number number number number \\
number number number number & number number number & number number  number \\
\noalign{\smallskip}\hline
\end{tabularx}
\begin{tablenotes}
      \small
      \item This is where authors provide additional information about the data, including whatever notes are needed.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\noalign{\smallskip}
\multicolumn{4}{l}{\textbf{Counselor}} \\
\noalign{\smallskip}

@@

\rowcolor{lightgraycol}
\noalign{\smallskip}
\multicolumn{4}{l}{\textbf{Patient}} \\
\noalign{\smallskip}
CT & Change Talk & Statements that express the patient’s desire, ability, reasons, need for, or commitment to (intentions, plans, and action steps) changing their behavior & ``I will try to buy less junk food.''\\
ST & Sustain Talk & Statements that express the patient’s desire, ability, reasons, need for, or commitment to (intentions, plans, and action steps) to maintain the status quo or not change their behavior  & ``I didn’t get to the gym this week.''\\
HUPO	 & High uptake other & An utterance that develops the topic of the conversation but is about non-target behaviors or interruptions & ``Yeah because the mentor comes and they take off and they go someplace for a little while.''\\
HUPW & High uptake weight & A turn that does develop the topic of the conversation. High Uptake statements include: weight related statements about actions of commitment, change talk, and ambivalence that occurred in the past, patient questions to the counselor, and session interruptions by persons who are not an active part of the treatment session. & ``Support is always good.  You know that’s a key factor.  Mm-hmm.''\\
LUP & Low uptake  & an utterance that does not develop the topic of conversation but still allows it to continue & ``Mm-hmm.  Right.''\\
\hline
\end{longtable}
\end{small}

@@

\begin{sidewaystable}
\vspace{32\baselineskip}

\caption{Hidden Markov Model Emission Matrices}
\label{tab:emission}
\begin{tabularx}{\textwidth}{lXXXp{0.4cm}XXXXXXXXXXXXXXXXXXX}
\hline\noalign{\smallskip}
State & AF & AR & EA & GIN- FON & GIN- FOP & QEB & QEC- HTP & QEC- MLP & QEF & QE- ST & QO & RC- HTP & RC- MLP & RO & RST & SO & SPT & SS & SUM & HU- PO & HU- PW & LUP \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\rowcolor{lightgraycol}
\multicolumn{23}{l}{\textbf{Successful  Sequences}} \\

High Motivation & 12\% & 5\% & 4\% & 0\% & 3\% & 0\% & 0\% & 1\% & 0\% & 0\% & 1\% & 29\% & 17\% & 1\% & 7\% & 2\% & 5\% & 6\% & 6\% & 0\% & 0\% & 0\% \\

High Receptivity & 15\% & 2\% & 5\% & 0\% & 18\% & 1\% & 16\% & 5\% & 3\% & 1\% & 0\% & 1\% & 0\% & 6\% & 5\% & 3\% & 3\% & 7\% & 4\% & 4\% & 1\% & 1\% \\

Moderate Receptivity & 2\% & 1\% & 14\% & 0\% & 8\% & 1\% & 20\% & 9\% & 5\% & 1\% & 2\% & 2\% & 0\% & 1\% & 0\% & 1\% & 0\% & 5\% & 4\% & 5\% & 2\% & 16\% \\

Low Receptivity & 4\% & 1\% & 17\% & 0\% & 3\% & 1\% & 11\% & 0\% & 2\% & 0\% & 0\% & 5\% & 3\% & 3\% & 3\% & 0\% & 1\% & 7\% & 1\% & 6\% & 0\% & 28\% \\

Active Feedback & 1\% & 1\% & 3\% & 0\% & 7\% & 1\% & 0\% & 9\% & 3\% & 0\% & 1\% & 0\% & 0\% & 0\% & 3\% & 1\% & 0\% & 1\% & 1\% & 10\% & 12\% & 47\% \\

\rowcolor{lightgraycol}
\multicolumn{23}{l}{\textbf{Unsuccessful  Sequences}} \\

Ambivalent & 13\% & 5\% & 4\% & 1\% & 6\% & 0\% & 1\% & 5\% & 0\% & 2\% & 2\% & 20\% & 7\% & 2\% & 12\% & 3\% & 4\% & 5\% & 6\% & 0\% & 2\% & 0\% \\

Avoidant  & 3\% & 1\% & 6\% & 0\% & 11\% & 7\% & 8\% & 1\% & 3\% & 2\% & 2\% & 1\% & 1\% & 5\% & 4\% & 0\% & 1\% & 2\% & 0\% & 11\% & 4\% & 29\% \\

\noalign{\smallskip}\hline
\end{tabularx}

@@

\caption{Hidden Markov Model Transition Matrices}
\label{tab:transition}  
\begin{tabularx}{\textwidth}{XXXXXX}
\hline\noalign{\smallskip}
State & High Motivation & High Receptivity & Moderate Receptivity & Low Receptivity & Active Feedback \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\rowcolor{lightgraycol}
\multicolumn{6}{l}{\textbf{Successful  Sequences}} \\
High Motivation & 2\% & 9\% & 24\% & 24\% & 41\% \\
High Receptivity & 7\% & 9\% & 20\% & 25\% & 39\% \\
Moderate Receptivity  & 8\% & 19\% & 24\% & 23\% & 27\% \\
Low Receptivity  & 11\% & 26\% & 28\% & 18\% & 17\% \\
Active Feedback  & 25\% & 34\% & 20\% & 15\% & 6\% \\
\rowcolor{lightgraycol}
\multicolumn{6}{l}{\textbf{Unsuccessful  Sequences}} \\
& Ambivalent & Avoidant & & & \\
Ambivalent & 16\% & 84\% & & & \\
Avoidant & 39\% & 61\% & & & \\
\noalign{\smallskip}\hline
\end{tabularx}
\end{sidewaystable}

@@

\begin{table}
\begin{threeparttable}
\caption{Frequent communication patterns in successful and unsuccessful patient-counselor communication sequences.}
\label{tab:patterns}   
\begin{tabularx}{\textwidth}{p{3cm}XX@{\extracolsep{4pt}}p{3cm}XX}
\hline\noalign{\smallskip}
\multicolumn{3}{c}{Successful} & \multicolumn{3}{c}{Unsuccessful} \\
\noalign{\smallskip}\cline{1-3} \cline{4-6}\noalign{\smallskip}
LUP & 573 & 52.0\% & LUP & 118 & 45.7\%  \\
RCHTP & 398 & 36.1\% & RCHTP & 87 & 33.7\% \\ 
\multicolumn{1}{r}{LUP, RCHTP} & 224 & 20.3\% & \multicolumn{1}{r}{LUP, RCHTP} & 45 & 17.4\% \\
QECHTP & 339 & 30.8\% & GINFOP & 74 & 28.7\% \\
\multicolumn{1}{r}{LUP, QECHTP} & 184 & 16.7\% & \multicolumn{1}{r}{LUP, GINFOP} & 44 & 17.1\% \\
AF & 314 & 28.5\% & RST & 70 & 27.1\% \\
\multicolumn{1}{r}{LUP, AF} & 166 & 15.1\% & \multicolumn{1}{r}{LUP, RST} & 30 & 11.6\% \\
EA & 314 & 28.5\% & AF & 68 & 26.4\% \\
\multicolumn{1}{r}{LUP, EA} & 188 & 17.1\% & EA & 48 & 18.6\% \\
GINFOP & 244 & 22.1\% & \multicolumn{1}{r}{LUP, EA} & 28 & 10.9\% \\
\multicolumn{1}{r}{LUP, GINFOP} & 143 & 13.0\% & QECHTP & 45 & 17.4\% \\
RCMLP & 228 & 20.7\% & RCMLP & 39 & 15.1\% \\
\multicolumn{1}{r}{LUP, RCMLP} & 121 & 11.0\% & QEB & 38 & 14.7\% \\
QECMLP & 200 & 18.1\% & RO & 30 & 11.6\% \\
RST & 174 & 15.8\% & QECMLP & 30 & 11.6\% \\
\multicolumn{1}{r}{LUP, RST} & 114 & 10.3\% & SUM & 29 & 11.2\% \\
RCHTP, QECHTP & 154 & 14.0\% & SS & 28 & 10.9\% \\
SUM & 138 & 12.5\% & RCHTP, GINFOP & 27 & 10.5\% \\
LUP, SS & 112 & 10.2\% & HUPO & 47 & 18.2\% \\
HUPO & 173 & 15.7\% &  &  &  \\ 
\noalign{\smallskip}\hline
\end{tabularx}
\begin{tablenotes}
      \small
      \item \textit{Note:} Patterns that are aligned to the right are included in the immediately preceding pattern count. In these patterns, a counselor behavior was paired with a patient low uptake/facilitative comment, which is a marker of patient attention to the conversation and feedback suggesting the line of discussion may continue.
\end{tablenotes}
\end{threeparttable}
\end{table}
